### 2016-11-18 README.Rmd
Update README

>>>>

Here is a map of all counties with flood events listed in the NOAA Storm Events database near the time and location of Hurricane Floyd:

```{r}
map_event_exposure(storm_id = "Floyd-1999", event_type = "flood")
```

Here are all the counties with tornado events listed for the same storm:

```{r}
map_event_exposure(storm_id = "Floyd-1999", event_type = "tornado")
```
